IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-01 assets/waveform_wpt_multisine.tex
:bento: Update assets

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213594256269\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	4.47213594337198\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.0184995683160857\\
2	4.47209768702344\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.129245877350812\\
2	4.47026793562064\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.22062490140461e-05\\
2	1.39192509615866e-05\\
3	0.000167256169027754\\
4	4.30544303806377\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	9.33422606187999e-05\\
2	0.00147978695861402\\
3	0.00191364123320196\\
4	4.17157348848167\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.79407563422514e-05\\
2	1.85714620268948e-05\\
3	1.93369863129044e-05\\
4	2.05312064086965e-05\\
5	2.39372760743564e-05\\
6	0.000270300028092872\\
7	0.0016215086351542\\
8	0.0160756710767743\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.10931097834311e-05\\
2	0.000139552824561586\\
3	0.000276023439508691\\
4	0.00106782286234867\\
5	0.00351285453513694\\
6	0.00648184617722918\\
7	0.107736181700373\\
8	0.176305935466697\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.1710720676869e-05\\
2	2.17376236559091e-05\\
3	2.17546727036312e-05\\
4	2.17704747375875e-05\\
5	2.1794882595919e-05\\
6	2.18143527307804e-05\\
7	2.18457881093868e-05\\
8	2.19305951527728e-05\\
9	2.19328455198334e-05\\
10	2.21325751565748e-05\\
11	2.22071274039942e-05\\
12	2.25919792561307e-05\\
13	2.32407144765052e-05\\
14	3.96822628633167e-05\\
15	7.14362303625945e-05\\
16	0.000113723656309437\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.55678240861943e-05\\
2	2.83329978735535e-05\\
3	0.000111062823999827\\
4	0.000152254112563635\\
5	0.000208409153895756\\
6	0.000340769670268019\\
7	0.000442331617111308\\
8	0.000478575211543757\\
9	0.000624300142407434\\
10	0.00101777812439063\\
11	0.00411301301403382\\
12	0.00600022404275364\\
13	0.0141022990885949\\
14	0.0215927071517045\\
15	0.0287996793460057\\
16	0.035646104685323\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,3.312in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	0.000331092582051402\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000301200841788861\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{No IRS: {\boldmath${s}$}$_{\mathrm{P}}$}

@@

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,2.598in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	8.31476170438795e-06\\
2	8.59623838841982e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.51350625686209e-05\\
2	2.5738452816653e-05\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.883in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=4.47213595499958,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.81401011150761e-05\\
2	7.63567990520219e-05\\
3	0.000347720308108743\\
4	1.20961154306659\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.00111014489403298\\
2	0.00243652079053788\\
3	0.00358274270606404\\
4	1.61181535442991\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.406193755485101\\
2	0.6086191375554\\
3	0.70781380097226\\
4	1.11700551493449\\
5	1.39413019214519\\
6	1.89924922357725\\
7	2.27606557910904\\
8	2.64280256661518\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.621345098069754\\
2	0.710296651693143\\
3	0.908023988477654\\
4	1.12050035456782\\
5	1.44244708781013\\
6	1.77492365099369\\
7	2.30702814170141\\
8	2.53638471775812\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=3.972in,
height=0.503in,
at={(0.666in,0.454in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=4.47213595499958,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.280439553353647\\
2	0.384605443069534\\
3	0.416114603863305\\
4	0.499024317224016\\
5	0.571268128602638\\
6	0.621900186283823\\
7	0.763344617968865\\
8	0.858693319856245\\
9	0.954356161751161\\
10	1.16907743761735\\
11	1.21561270661726\\
12	1.45089690540298\\
13	1.51204499963039\\
14	1.68681223326519\\
15	1.74569476977388\\
16	1.81071246294588\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.447567787711277\\
2	0.504906671531525\\
3	0.589458291557858\\
4	0.619646960375962\\
5	0.691059903147371\\
6	0.741736916016998\\
7	0.810826698348076\\
8	0.887751406400927\\
9	0.941910732226763\\
10	1.15698606523739\\
11	1.20259880483264\\
12	1.42353667332449\\
13	1.46532152628089\\
14	1.65027292091107\\
15	1.65828648619566\\
16	1.73730645060792\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
